J-Study manuscript

### 2023-01-25 writing/ms.Rmd
prepare to clone repo on other computer

---
title: "J-Study manuscript"
author: "Monica Thieu"
date: "5/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro

@@

- What research has been done on superior memory?
    - Superior memorizers
    - (MAYBE SCRATCH) savants?
    - Highly superior autobiographical memory
- What can studying trivia experts tell us that studying other superior memory groups doesn't?
    - Trivia expertise might be more likely to derive from innate memory differences than superior memorization, which tends to rely on becoming facile with a strategy
    - Trivia facts, as must anything else, must be encoded through episodic mechanisms, but once encoded, are considered squarely within the domain of semantic memory. Studying trivia memory can tell us a lot about the putative boundary between episodic and semantic memory
    - [@Brandt:2017cd]
- What research has been done on general knowledge capacity as its own memory construct?
- Thus, the current study

>>>>

---
title: "J-Study manuscript"
author: "Monica Thieu"
date: "Updated `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
require(tidyverse)
require(magrittr)
load(here::here("ignore", "data", "plots_ms.rda"))
```

# Figures and captions

## Figure 3

```{r}
plot_demos
```

```{r}
plot_expertise_hist
```

## Figure 4

```{r}
plot_fact_by_expertise
```

## Figure 5

```{r}
plot_coefs_fact_by_pic
```

```{r}
plot_fixef_fact_by_pic
```

```{r}
plot_pic_by_expertise
```

## Figure 6

```{r}
plot_coefs_fact_by_source
```

```{r}
plot_fixef_fact_by_source
```

```{r}
plot_source_by_expertise
```

<!--
# OLD STUFF I FOUND IN HERE: Intro

@@

- What research has been done on superior memory?
    - Superior memorizers
    - (MAYBE SCRATCH) savants?
    - Highly superior autobiographical memory
- What can studying trivia experts tell us that studying other superior memory groups doesn't?
    - Trivia expertise might be more likely to derive from innate memory differences than superior memorization, which tends to rely on becoming facile with a strategy
    - Trivia facts, as must anything else, must be encoded through episodic mechanisms, but once encoded, are considered squarely within the domain of semantic memory. Studying trivia memory can tell us a lot about the putative boundary between episodic and semantic memory
    - [@Brandt:2017cd]
- What research has been done on general knowledge capacity as its own memory construct?
- Thus, the current study
-->
